
\documentclass[12pt]{report}
\usepackage{geometry}
\usepackage{titling}

\geometry{margin=1in}

\newcommand{\subtitle}[1]{
	\posttitle{
		\par\end{center}
		\begin{center}\large#1\end{center}
		\vskip0.5em}
}

\title{Project Specification}
\subtitle{CS 383 - Homework 1 - Group 3}

\author{
Mason Fabel \\
\and Morgan Holbart \\
\and Ronald Rodriguez \\
\and Tessa Saul \\
\and Lance Wells \\
\and Zachary Yama \\
}

\date{\today}

\begin{document}

\maketitle

\chapter{Use Cases}

\begin{section}{Morgan Holbart}
\begin{subsection}{Crafting Items}
Actor: Player

Precondition:
\begin{enumerate}
\item The player has the necessary ingredients to make a crafted item.
\end{enumerate}

Summary: The PLayer takes ingredients for a crafted item and expends them to
recieve a different item.

Steps:
\begin{enumerate}
\item Player opens crafting menu.
\item Player selects crafting recipe.
\item The items for the recipe are destroyed.
\item The crafted item is placed in the player's inventory.
\end{enumerate}
\end{subsection}

\begin{subsection}{Dialog}
Actors: Player, NPC

Preconditions:
\begin{enumerate}
\item The player is currently able to interact with the target.
\item The target wishes to interact with the player.
\item The NPC has something to say.
\end{enumerate}

Summary: A player tries to initiate conversation with an NPC.

Steps:
\begin{enumerate}
\item The player interacts with the NPC.
\item The NPC responds to the player.
\item The player can respond based on user input.
\item When the NPC runs out of things to say, the dialog ends.
\end{enumerate}
\end{subsection}

\begin{subsection}{Opening and Closing Inventory}
Actor: Player

Preconditions: 
\begin{enumerate}
\item Player can currently perform the action of opening/closing inventory.
\end{enumerate}

Steps:
\begin{enumerate}
\item The player presses the input to open/close the inventory.
\item The inventory is loaded and displayed or closed .
\end{enumerate}
\end{subsection}

\begin{subsection}{Starting Game}
Actor: Player

Preconditions: 
\begin{enumerate}
\item Player is in the menu.
\item Player is selecting the start game button.
\end{enumerate}

Steps:
\begin{enumerate}
\item The player presses the input to start the game.
\item The game loads the user save data.
\item The game loads the lobby level with regard to the user save data.
\end{enumerate}
\end{subsection}

\begin{subsection}{Reload Weapon}
Actor: Player

Preconditions: 
\begin{enumerate}
\item Player has a weapon equipped that can reload.
\item Player has ammo to reload with.
\end{enumerate}

Steps:
\begin{enumerate}
\item Press the reload button.
\item Subtract ammo from the stored ammo.
\item Add the subtracted ammo to the current ammo.
\end{enumerate}
\end{subsection}

\begin{subsection}{Start Dungeon}
Actor: Player

Preconditions:
\begin{enumerate}
\item Player is the leader of a dungeon group.
\item Player is currently connected with all party members.
\item Party members have all selected the ready button.
\item Party members all have adequate reputation to do the dungeon.
\end{enumerate}

Steps:
\begin{enumerate}
\item Player interacts with the computer he wishes to enter.
\item All other players are in party already, or join the party through the
computer.
\item The party leader presses the start dungeon button.
\end{enumerate}
\end{subsection}

\begin{subsection}{Attacking (with Ronnie Rodriguez)}
Actor: Player

Preconditions:
\begin{enumerate}
\item Player has a valid weapon to use equipped.
\item Player has ammo or durability to use equipped weapon.
\item Player is able to attack (not in a current dialog/other interaction).
\end{enumerate}

Steps:
\begin{enumerate}
\item The player presses the input to attack.
\item Ammunition/Durability is subtracted.
\item The weapon animation/effects/etc are instantiated.
\item Amount of damage done per hit is subtracted from the enemy's total hit
points.
\end{enumerate}
\end{subsection}
\end{section}

\begin{section}{Ronnie Rodriguez}
\begin{subsection}{Opening Doors}
Actor: Player

Preconditions:
\begin{enumerate}
\item The door is able to be opened.
\end{enumerate}

Summary: Player tries to open a door to access area on the other side. 

Steps:
\begin{enumerate}
\item The player approaches the door.
\item Once close enough to the door, the player presses input to attempt to
enter.
\item If door is unlocked, door opens and player is granted access to the
area on the other side.
\item If door is locked, a "locked" or "Need Key" prompt is output to the
screen.
\end{enumerate}
\end{subsection}

\begin{subsection}{Killing an Enemy}
Actor: Player, Enemy

Preconditions:
\begin{enumerate}
\item Player is able to attack enemy.
\item The enemy has a low enough armor rating to where the player's attacks
are damaging it.
\item Enemy can be killed.
\end{enumerate}

Summary: Player attacks enemy with weapon until enemy's hit points are
completely depleted.

Steps:
\begin{enumerate}
\item Player gets close enough to enemy to attack either ranged or melee.
\item Player depletes enemy's hit points before player's hit points are
depleted by enemy.
\item Enemy ceases attacking and enemy death animation is instantiated.
\end{enumerate}
\end{subsection}

\begin{subsection}{Using Keys and Codes}
Actor: Player

Preconditions:
\begin{enumerate}
\item A door the player wishes to go through is currently locked.
\item Player has needed key/code to unlock door in inventory.
\end{enumerate}

Summary: Player uses found keys or codes to unlock locked doors.

Steps:
\begin{enumerate}
\item Player gets close enough to door to interact with it.
\item Player presses input to initialize unlocking procedure.
\item ``Unlock door with key/code?'' prompt is displayed on the screen along
with Yes or No choice.
\item Player chooses Yes or No option.
\item If player chooses No, prompt closes, door remains locked, and key/code
remains in inventory.
\item If player chooses Yes, ``Door Unlocked'' prompt displays to screen,
door unlocks, and key/code is removed from inventory.
\item Player initiates Open Door procedure (see above).
\end{enumerate}
\end{subsection}

\begin{subsection}{Taking Damage}
Actor: Player

Preconditions:
\begin{enumerate}
\item Player is being attacked by enemy.
\item Player has a low enough armor rating to where they are able to be
damaged by current enemy.
\end{enumerate}

Summary: Player is being attacked and is losing health/HP.

Steps:
\begin{enumerate}
\item Player is attacked by enemy.
\item Depending on strength of enemy, an amount of damage is done to the
player.
\item Amount of hit points directly related to amount of damage done by
enemy is subtracted from the player's total remaining health..
\end{enumerate}
\end{subsection}

\begin{subsection}{Moving Items in Inventory}
Actor: Player

Preconditions:
\begin{enumerate}
\item Player has an item(s) in inventory they'd like to rearrange.
\end{enumerate}

Summary: Player can manually rearrange items in inventory for better
organization and quicker use.

Steps:
\begin{enumerate}
\item Player presses input to open inventory.
\item Game action is paused while inventory is open.
\item Player selects ``Rearrange'' option from inventory sidebar.
\item Player presses input to select item they wish to move.
\item Item selected is highlighted.
\item Player navigates inventory and presses input to choose inventory slot
they would like to move item to.
\item If selected inventory slot is empty, item is moved to that slot,
original slot holding the item is now empty.
\item If selected inventory slot is occupied, selected item will swap places
with item in occupied slot. 
\end{enumerate}
\end{subsection}
\end{section}

\begin{section}{Tessa Saul}
\begin{subsection}{Moving through Areas}
Actor: Player

Preconditions:
\begin{enumerate}
\item The player has the area being moved to unlocked or available to him.
\end{enumerate}

Summary: The player accepts a prompt moving him to a new dungeon, floor, or
back to the lobby.

Steps:
\begin{enumerate}
\item The player uses an object (door/computer).
\item Player hits yes to the prompt on whether or not to use it.
\item The player is moved from the current location to the new location.
\item The new level is constructed (if a dungeon), or loaded (if the lobby)
and the player is placed in it.
\end{enumerate}
\end{subsection}

\begin{subsection}{Selling Items}
Actor: Player, Shopkeeper

Preconditions:
\begin{enumerate}
\item The player has an item that the shopkeeper is willing to buy.
\item The shopkeeper has sufficient currency for the transaction.
\end{enumerate}

Summary: Player exchanges an item for currency with a shopkeeper.

Steps: 
\begin{enumerate}
\item Player approaches shopkeeper.
\item Player engages shop.
\item Player selects item from their inventory to sell.
\item Item is given to shopkeeper, currency is taken from shopkeeper and
given to player.
\end{enumerate}
\end{subsection}

\begin{subsection}{Buying Items}
Actor: Player, Shopkeeper

Preconditions:
\begin{enumerate}
\item The shopkeeper has an item that the player is willing to buy.
\item The player has sufficient currency for the transaction.
\end{enumerate}

Summary: Player exchanges an currency for item with a shopkeeper.

Steps: 
\begin{enumerate}
\item Player approaches shopkeeper.
\item Player engages shop.
\item Player selects item from shopkeeper's inventory to buy.
\item Item is given to player, currency is taken from player and given to
shopkeeper.
\end{enumerate}
\end{subsection}

\begin{subsection}{Picking Up Items}
Actor: Player

Precondition:
\begin{enumerate}
\item The player has an empty slot big enough for the item in their
inventory.
\end{enumerate}

Summary: A player's action transfers an item from the environment into their
inventory.

Steps:
\begin{enumerate}
\item Player approaches item.
\item Player engages item.
\item Item is removed from environment.
\item Item is placed in the player's  inventory.
\end{enumerate}
\end{subsection}
\end{section}

\begin{section}{Lance Wells}
\begin{subsection}{Die}
Actor: Player

Preconditions:
\begin{enumerate}
\item The player is actively playing the game and has just taken
fatal damage.
\end{enumerate}

Summary: The player has taken fatal damage and now proceeds to die with a
restart option.

Steps:
\begin{enumerate}
\item The player takes some form of fatal damage.
\item The player is then frozen on the spot, unable to interact with any
surroundings.
\item The player proceeds into a possible death animation for a few seconds.
\item The player must then choose from a pop-up menu how they would like to
proceed.
\end{enumerate}
\end{subsection}

\begin{subsection}{Leave a Dungeon}
Actor: Player

Preconditions:
\begin{enumerate}
\item The player currently inside of a dungeon.
\end{enumerate}

Summary: The player leaves a dungeon through the use of a menu.

Steps:
\begin{enumerate}
\item1 The player presses a button that requests to leave the current
dungeon.
\item A confirmation window appears that prompts the player if they would
like to proceed.
\item If the player chooses to leave the dungeon again, they will switch
to the main lobby.
\item If the player chooses to remain in the dungeon, the prompt window will
close.
\end{enumerate}
\end{subsection}

\begin{subsection}{Use an Item}
Actor: Player

Preconditions:
\begin{enumerate}
\item The player currently has some usable item.
\end{enumerate}

Summary: The player actively uses some usable item.

Steps:
\begin{enumerate}
\item The player either opens their inventory, or currently has a usable
item equipped in some fashion.
\item The player will indicate the specific item that they wish to use
through some button combination or key press.
\item The item then is removed from the player's inventory.
\item The item's effect then occurs.
\end{enumerate}
\end{subsection}

\begin{subsection}{Change Current Weapon}
Actor: Player

Preconditions:
\begin{enumerate}
\item The player currently has two or more selectable weapons.
\end{enumerate}

Summary: The player indicates a weapon to change and does so.

Steps:
\begin{enumerate}
\item The player either opens their inventory or currently has two or more
``equipped'' weapons.
\item The player indicates a request as to which weapon to switch to through
some key press.
\item The player's active weapon is considered to no longer be active and
potentially returned to their inventory.
\item The player then either equips the newly indicated weapon or that new
weapon is considered to be active.
\end{enumerate}
\end{subsection}

\begin{subsection}{Close the Game}
Actor: Player

Preconditions:
\begin{enumerate}
\item The player has access to the menu that allows for the game to close.
\end{enumerate}

Summary: The player closes the game via an in-game menu option.

Steps:
\begin{enumerate}
\item The player indicates a request to leave via some button press.
\item A pop-up window appears requesting the player to confirm that they
would like to close the game.
\item If the player should proceed, the program will (potentially) auto-save
and then close entirely.
\end{enumerate}
\end{subsection}

\begin{subsection}{Select an Item from Inventory}
Actor: Player

Preconditions:
\begin{enumerate}
\item The player is currently at the main menu.
\end{enumerate}

Summary: The player selects an option via some button press that reacts
appropriately.

Steps:
\begin{enumerate}
\item The player is selects some menu option with a button press.
\item The menu either then disappears and is replaced with another menu, or
closes and reacts according to the user's request.
\end{enumerate}
\end{subsection}

\begin{subsection}{Level Up}
Actor: Player

Preconditions:
\begin{enumerate}
\item The player has all requirements to achieve an increase in level
\item The player is currently in the lobby.
\end{enumerate}

Summary: The player moves (literally) up a level in progress.

Steps:
\begin{enumerate}
\item The player is informed through some message that they are now eligible
for an advancement in their level.
\item The player makes a request with some NPC that they would like to
advance a level.
\item The player's current reputation is now adjusted to mirror their
current level.
\item The player is physically adjusted up one level of the office building.
\end{enumerate}
\end{subsection}

\begin{subsection}{Increase Stats}
Actor: Player

Preconditions:
\begin{enumerate}
\item The player has alterable stats that can be changed through some
action.
\end{enumerate}

Summary: The player makes a request for a stat adjustment through some
method and is altered in kind.

Steps:
\begin{enumerate}
\item The player makes a request to change stats through an item being
equipped or unequipped or otherwise.
\item The player's request is processed and the player's stats are changed
to mirror the request.
\end{enumerate}
\end{subsection}
\end{section}

\begin{section}{Zachary Yama}
\begin{subsection}{Equip and Item}
Actor: Player

Precondition: 
\begin{enumerate}
\item The player has the status to equip the item. 
\item The item is in their inventory.
\end{enumerate}

Summary: A player's action transfers an item from their inventory to their
equipment.

Steps:
\begin{enumerate}
\item Player has the item.
\item Player selects an equip action.
\item Item is removed from inventory.
\item Item is placed in equipment.
\item Item(s) currently in equipment occupying the spaces required to eqiup
the new item are moved to inventory.
\item If the item(s) being swapped out assume more inventory space then the
player has, ignore/undue the equip action.
\end{enumerate}
\end{subsection}

\begin{subsection}{Look at Stats}
Actor: Player

Precondition:
\begin{enumerate}
\item The player selects the status menu icon.
\end{enumerate}

Summary: Input from the player opens the status menu.

Steps:
\begin{enumerate}
\item Player selects stats menu icon.
\item The status window is opened.
\item Status information is read and loaded into the window.
\item Stat alteration actions are deactivated or activated depending on
status point availability.
\end{enumerate}
\end{subsection}

\begin{subsection}{Look at Map}
Actor: Player

Precondition:
\begin{enumerate}
\item The player toggles the map menu icon.
\end{enumerate}

Summary: Input form the player opens the map menu.

Steps:
\begin{enumerate}
\item The player selects the map menu icon.
\item The map menu is opened.
\item Player coordinates are set as a map rendering position.
\item The surrounding level content is loaded into the map.
\item Explored content is displayed.
\end{enumerate}
\end{subsection}

\begin{subsection}{Hit a Monster}
Actor: Player, Monster

Precondition:
\begin{enumerate}
\item The player has attacked.
\item The player's attack hitbox hit a monster.
\end{enumerate}

Summary: A player has performed the action to attack, and successfully hit
an enemy.

Steps:
\begin{enumerate}
\item Calculate active collisions to determine if the enemy was hit.
\item The damage delt is calculated based on player and monster attributes.
\item Damage is deducted from the monster's health. 
\item Any elemental or otherwise behavior altering elements are applied to
the monster.
\item  If the monster's health is zero, the monster's status is changed to
dead.
\end{enumerate}
\end{subsection}

\begin{subsection}{Kill a Monster}
Actor: Player, Monster

Precondition:
\begin{enumerate}
\item The player has reduced a monster's health to zero.
\end{enumerate}

Summary: A monsters health has been reduced to zero, and is dead.

Steps:
\begin{enumerate}
\item The monster's hitbox is no longer active.
\item Any active AI is no longer active.
\item A death animation is played.
\item The displayed sprite is changed to represent a dead enemy.
\item The status of the enemy is set to dead, and any ressurection elements
are set to applicable.
\item The enemy is determined to be permanatly dead.
\item Any items to drop are generated.
\item The item is instanciated and dropped.
\end{enumerate}
\end{subsection}

\begin{subsection}{Level Up}
Actor: Player

Precondition:
\begin{enumerate}
\item The player has the required experience (Reputation?) to level up.
\end{enumerate}

Summary: A player has gained enough experience to increase their level. 

Steps:
\begin{enumerate}
\item The experience level is compared to the amount required to level up. 
\item If the experience level is high enough, the player's level is
increased by 1.
\item Usable stats points are awarded to the stats class. 
\item The expereince bar size is recalculated.
\item The current amount of experience is reduced to zero plus any
additional experience carryover.
\item A levelup indicator is displayed.
\item Health is regenerated.
\end{enumerate}
\end{subsection}

\begin{subsection}{Increase Stats}
Actor: Player

Precondition:
\begin{enumerate}
\item The player has available status points to spend.
\end{enumerate}

Summary: A player has unspent stats points and expends them. 

Steps:
\begin{enumerate}
\item The player selects a stat to increase.
\item The amount of points required to increase a stat are calculated.
\item If a stat requires more points than available, its increase action is
deactivated.
\item If there are enough points to expend, available stats points are
reduced accordingly.
\item The stat is increased. 
\item Steps 1-5 are repeated for every action until all stats points are
expened.
\item Any remaining points are saved.
\end{enumerate}
\end{subsection}
\end{section}

\end{document}
